Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-28 latex/afm-cs-main.tex
Make the text in the metrics color legend white.
Update on Overleaf.

\subsection{Feedforward Control}\label{sec:ff_control}
Unfortunately, as the bottom row of plots in
Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong
cross-coupling from the horizontal plane to the $Z$ axis (the coupling
from $u_Z$ to the $X$ and $Y$ axes is very weak, and so is not shown).
Our SISO control scheme does little to attenuate the resonances of
$G_{Z,u_X}$ and $G_{Z,u_Y}$. In particular, there are modes in both
these transfer functions at 215 and 505 Hz that do not appear in a
SISO model of $G_{X,u_X}$ or $G_{Y,u_Y}$.

@@

For raster scanning, we set $F_X=F_Y=1$ and instead take advantage of
the periodicity of the $X$-axis reference, which is a triangle wave.
We modify the triangle wave to a truncated Fourier series, where each
Fourier coefficient is scaled by the inverse of the closed-loop FRF at
the corresponding frequency. See, e.g., \cite{clayton_review_2009} for
more details on this strategy. We truncate this series such that the
highest frequency is smaller than 200 Hz, which means that we should
never excite the problematic $G_{Z,u_X}$ modes. This scheme implies
that the effective bandwidth of the $X$-axis controller is higher
while raster scanning than while CS-scanning. On the other hand, it
also implies that for faster scan rates, fewer Fourier
coefficients are used, and so the approximation to a triangle wave is
worse.

\section{Metrics}\label{sec:rdi}
In section~\ref{sec:results} we use three metrics to assess our
results. The first two seek to quantify image quality between two images.
Define a master image as $X$ and a reconstruction or corrupted version
as $Y$, with each having $s\times h=m$ pixels. Let $x=\textrm{vec}(X)$
and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master
image $x$. Then the peak signal to noise ratio (PSNR) is given by
\begin{equation*}
  \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
  {\sqrt{\frac{1}{m} \sum_{i=1}^{m}( x_{i} - y_{i})^2 }}.
\end{equation*}

The goal of the SSIM is to compare two image's structure,
luminescence, and contrast and is built up from the means ($\mu_x$ and
$\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and
covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$. The SSIM definition used in this paper is
\begin{equation*}
  \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
  {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
\end{equation*}
where the constants $C_1$ and $C_2$ are regularizing constants to
prevent singularity if, e.g., $\mu_x=\mu_y=0$. We use the default
values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and
${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range. In general
two images which are identical will yield an infinite PSNR and an SSIM
of 1.

@@

\begin{figure}[t!]
  \centering
  % \includesvg[width=0.7\columnwidth]{figures/baseline_errors_aligned_1Hz.svg}
  \includesvg[width=0.7\columnwidth]{figures/baseline_errors_1and6.svg}
  \caption{Errors between the first and sixth raster scans in a
    sequence of six 1.0~Hz raster scans. (left) Errors without
    alignment (right) The same data but aligned via cross
    correlation.}
  \label{fig:baseline_errors}
\end{figure}

\subsection{A new metric}
The PSNR and SSIM metrics only assess the similarity of two images.
However, in AFM imaging, pure image quality is not the only concern,
particularly for delicate samples. What is needed is a figure of merit
for how much damage was done to a specimen during the imaging process.
While damage to the specimen is not really a concern while imaging a
hard calibration grating, it plays a prominent role for biological
samples~\cite{ando_highspeed_2008}, though damage to the probe itself
is still a concern. In general, the faster the scan rate, the more
difficulty the $Z$-axis control will have in following the sample
surface, which results in a larger $Z_d$ over more time. The actual
damage done by a given $Z_d$ will depend on the spring constant of the
cantilever and the softness of the specimen. Nonetheless, we propose a
metric, which we call the Relative Damage Index (RDI) which computes
the power in the deflection signal for a given scan. That is,

\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}
\end{align}
The idea behind the RDI is that increased scan rates lead to larger
deflection signals (and thereby increased force into the specimen) at
each surface feature, which the RDI accumulates.

\section{Experimental Results}\label{sec:results}
We compared $\mu$-path scanning to two scenarios. First, we compare it
to full resolution raster scans at several scan rates in
Sec.~\ref{sec:cp_full}. Second, we compare to coarse raster scans in
Sec.~\ref{sec:cp_subline}.

\subsection{Comparison to full raster}\label{sec:cp_full}
We took scans of a Ted Pella CS-20NG sample grating over an area with
holes on a 500 nm pitch. The holes are 20 nm deep. We scanned 5 micron
by 5 micron images using standard raster scans with 512 lines. For the
raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
10~Hz. We also took $\mu$-path scans with densities at 12.5\% and
25\% and reconstructed 512 by 512 pixel images. The CS scans were
taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
2.0~Hz, 4.0~Hz, 5.0~Hz and 8.0~Hz. For all CS scans, the $\mu$-paths are
$\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$
pixels.

>>>>

\subsection{Feedforward Control}\label{sec:ff_control}
As the bottom row of plots in
Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong
cross-coupling from the horizontal plane to the $Z$ axis (the coupling
from $u_Z$ to the $X$ and $Y$ axes is very weak, and so is not shown).
Our SISO control scheme does little to attenuate the resonances of
$G_{Z,u_X}$ and $G_{Z,u_Y}$. In particular, there are modes in both
these transfer functions at 215 and 505 Hz that do not appear in a
SISO model of $G_{X,u_X}$ or $G_{Y,u_Y}$.

@@

For raster scanning, we set $F_X=F_Y=1$ and instead take advantage of
the periodicity of the $X$-axis reference, which is a triangle wave.
We modify the triangle wave to a truncated Fourier series, where each
Fourier coefficient is scaled by the inverse of the closed-loop FRF at
the corresponding frequency. See, e.g., \cite{clayton_review_2009} for
more details on this strategy. We truncate this series such that the
highest frequency is smaller than 200 Hz, which means that we should
never excite the problematic $G_{Z,u_X}$ modes. This scheme implies
that the effective bandwidth of the $X$-axis controller is higher
while raster scanning than while CS-scanning. On the other hand, it
also implies that for faster scan rates, fewer Fourier
coefficients are used, and so the approximation to a triangle wave is
worse, leading to scans which do not cover the entire intended range..

\section{Metrics}\label{sec:rdi}
In this section we introduce the three metrics used to assess our
results in Sec.~\ref{sec:results}. The first two seek to quantify image quality between two images.
To that end, define a master image as $X$ and a reconstruction or corrupted version
as $Y$, with each having $s\times h=m$ pixels. Let $x=\textrm{vec}(X)$
and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master
image $x$. The first metric is the peak signal to noise ratio (PSNR), given by
\begin{equation*}
  \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
  {\sqrt{\frac{1}{m} \sum_{i=1}^{m}( x_{i} - y_{i})^2 }}.
\end{equation*}

The second metric is the Structured Similarity Index Metrix (SSIM).
The goal of the SSIM is to compare two image's structure,
luminescence, and contrast and is built up from the means ($\mu_x$ and
$\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and
covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$. The SSIM definition used in this paper is
\begin{equation*}
  \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
  {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
\end{equation*}
where the constants $C_1$ and $C_2$ are regularizing constants to
prevent singularity if, e.g., $\mu_x=\mu_y=0$. We use the default
values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and
${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range. In general
two images which are identical will yield an infinite PSNR and an SSIM
of 1.

@@

\begin{figure}[t!]
  \centering
  % \includesvg[width=0.7\columnwidth]{figures/baseline_errors_aligned_1Hz.svg}
  \includesvg[width=0.9\columnwidth]{figures/baseline_errors_1and6.svg}
  \caption{Errors between the first and sixth raster scans in a
    sequence of six 1.0~Hz raster scans. (left) Errors without
    alignment (right) The same data but aligned via cross
    correlation.}
  \label{fig:baseline_errors}
\end{figure}

\subsection{A new metric}
The PSNR and SSIM metrics only assess the similarity of two images.
However, in AFM imaging, pure image quality is not the only concern,
particularly for delicate samples. While damage to the specimen is not really a concern while imaging a
hard calibration grating, it plays a prominent role for biological
samples~\cite{ando_highspeed_2008}, though damage to the probe itself
is still a concern even with hard samples. In general, the faster the scan rate, the more
difficulty the $Z$-axis control will have in following the sample
surface, which results in a larger $Z_d$ over more time. The actual
damage done by a given $Z_d$ will depend on the spring constant of the
cantilever and the softness of the specimen. To capture these concerns, we propose a
metric, which we call the Relative Damage Index (RDI) that computes
the power in the deflection signal for a given scan. The RDI,given by

\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2, \label{eqn:RDI}
\end{align}
accumulates the deflection signal as a measure of the net force applied to the specimen  over time.

\section{Experimental Results}\label{sec:results}
We compared $\mu$-path scanning to two scenarios: first to full resolution raster scans at several scan rates in
Sec.~\ref{sec:cp_full}, and second, to coarse raster scans in
Sec.~\ref{sec:cp_subline}.

\subsection{Comparison to full raster}\label{sec:cp_full}
We took scans of a Ted Pella CS-20NG sample grating over an area with
holes on a 500 nm pitch. The holes are 20 nm deep. We scanned 5 micron
by 5 micron images using standard raster scans with 512 lines. For the
raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
10~Hz. We also took $\mu$-path scans with densities at approximately 12.5\% and
25\% and reconstructed 512 by 512 pixel images. The CS scans were
taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
2.0~Hz, 4.0~Hz, 5.0~Hz and 8.0~Hz. For all CS scans, the $\mu$-paths are
$\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$
pixels.
